\documentclass[margin=1in, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\newsectionwidth{0pt} % Stops section indenting

% \usepackage[margin=1in]{geometry}

\begin{document}

%----------------------------------------------------------------------------------------
% YOUR NAME AND ADDRESS(ES) SECTION
%----------------------------------------------------------------------------------------

\name{Yuanzhe (Rijn) Bian\\ \\}

% If you don't want one of the addresses, simply remove all the text in the first or second \address{} bracket

\address{{\bf Software Engineer} \\ Meta Platforms} % Your address 1

\address{http://rijn.io/ \\ rijn@meta.com}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
% EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{EDUCATION}} \vspace{0.1in}

{\sl Bachelor of Science}, Mathematics \hfill Nov 2018 -- Dec 2018 \\
University of Illinois at Urbana - Champaign \hfill Champaign, IL, USA \\
College of Liberal Arts \& Science

{\sl Bachelor of Engineering}, Computer Science \hfill Aug 2016 -- Dec 2018 \\
University of Illinois at Urbana - Champaign \hfill Champaign, IL, USA \\
College of Engineering\\
GPA 3.98\\
Advisor: Stephen M. Herzog

{\sl Bachelor of Engineering}, Telecommunication Engineering (Transferred) \hfill Sep 2014 -- Jul 2016 \\
Nanjing University of Posts and Telecommunications \hfill Nanjing, Jiangsu, China \\
School of Communication and Information Engineering \\
GPA 3.7, Top 5\% \\
Advisor: Mingcheng Qin

Jinling High School, Nanjing, Jiangsu, China \hfill Jun 2014

High School Affiliated to Nanjing Normal University Shuren Campus, Nanjing, Jiangsu, China \hfill Jun 2011

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
% PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{EXPERIENCE}} \vspace{0.1in}

{\sl Meta Platforms} \hfill Feb 2019 -- Present \\
Software Engineer Internship \hfill Burlingame, CA
\vspace{0.05in}
\begin{itemize} \itemsep -2pt
\item Working on AR/VR.
\item Worked on Ads creation.
\end{itemize}

{\sl University of Illinois Research Park, EnterpriseWorks} \hfill Sep 2018 -- Dec 2018 \\
Software Engineer Internship \hfill Champaign, IL

{\sl Facebook} \hfill May 2018 -- Aug 2018 \\
Software Engineer Internship \hfill Menlo Park, CA
\vspace{0.05in}
\begin{itemize} \itemsep -2pt
\item Worked on Spatial Computing Team. Helped to improve the geolocation data visualization tool.
\item Designed and implemented an augmented reality navigation x-plat App. Worked with indoor localization group and map generation group. Fulfilled the group plan two months ahead of schedule.
\end{itemize}

{\sl Chirp Social Networking, Inc.} \hfill Feb 2018 -- Dec 2018 \\
Co-founder \hfill Champaign, IL

{\sl University of Illinois Research Park, EnterpriseWorks} \hfill Jan 2018 -- May 2018 \\
Software Engineer Internship \hfill Champaign, IL
\vspace{0.05in}
\begin{itemize} \itemsep -2pt
\item Designed manager system and SPA framework on Salesforce.
\end{itemize}

{\sl NextCapital Group} \hfill Sep 2017 -- Dec 2017 \\
Remote Software Engineer Internship \hfill Chicago, IL

{\sl NextCapital Group} \hfill Jun 2017 -- Aug 2017 \\
Software Engineer Internship \hfill Chicago, IL
\vspace{0.05in}
\begin{itemize} \itemsep -2pt
\item Front-end group. Maintained NextCapital's front-end software which is written in Angular and React.
\item Upgraded the unit test framework. Result in $>50\%$ time saving on the CI by applying the new environment.
\item Developed an intelligent report generator which can help the manager generating weekly target completion report by analyzing data from the time tracker automatically.
\item Collaborated with other interns to create a document generator which can generate the document based on the codebase.
\end{itemize}

{\sl UmiUni, LLC} \hfill Feb 2017 -- Nov 2017 \\
Co-founder \hfill Champaign, IL
\vspace{0.05in}
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Designed whole software architect. Participated and contributed to all projects, including design, programming, unit testing, code review and deployment planning. Developed back-end server powered by Node.js. Also developed front-end app by Vue.js, and contributed to the iOS App by RN.
\end{itemize}

{\sl Dexta Robotics, Inc.} \hfill Mar 2014 -- Present \\
Co-founder \hfill Shenzhen, China
\vspace{0.05in}
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Designed import devices for hand-motion detection, and designed the circuit board for these devices.
\item Designed a 2.4G wireless dongle for pulling data from Dexmo.
\item Developed an embedded system for Dexmo. Built the website.
\item Designed some steering motor circuit.
\end{itemize}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
% VOLUNTEER EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{VOLUNTEER EXPERIENCE}} \vspace{0.1in}

{\sl Nanjing University of Posts and Telecommunications} \hfill Apr 2015 -- Jun 2016 \\
Technical Supervisor \hfill Nanjing, China
\vspace{0.05in}
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Led a group and designed a high-performance distributed system to fetch data from official systems.
\item Designed a tunnel to cross LAN firewall.
\item Wrote a class that using computer vision and machine learning techniques to identify verification code.
\item Implemented a load-balancing RESTFul API service and a web-app that has one million PV per year.
\end{itemize}

{\sl Nanjing University of Posts and Telecommunications} \hfill Dec 2014 -- Jun 2015 \\
Student Lecturer at Student Association of Science and Technology \hfill Nanjing, China

{\sl Extreme Memory} \hfill Sep 2014 -- Jun 2016 \\
Web Designer \& Developer \hfill Nanjing, China
\vspace{0.05in}
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Designed an online application to teach users memorizing methods and provide online memory tests.
\item Wrote an SDK for native JavaScript for adding login, authorization and score submission API calls.
\item Wrote a server powered by Node.js and MySQL.
\end{itemize}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
% PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{PUBLICATIONS}} \vspace{0.1in}

See https://goo.gl/UWvADs for a research impact summary compiled by Google Scholar.

{\bf Conference Proceedings}

\begin{itemize}
\vspace{0.1in}

\item Dexmo: An Inexpensive and Lightweight Mechanical Exoskeleton for Motion Capture and Force Feedback in VR\\
{\sl X Gu, Y Zhang, W Sun, Y Bian, D Zhou, PO Kristensson}\\
Proceedings of the 2016 CHI Conference on Human Factors in Computing Systems

\item Opico: A Study of Emoji-first Communication in a Mobile Social App\\
{\sl S Khandekar, J Higg, Y Bian, C Won Ryu, J O Talton Iii, R Kumar}\\
Companion Proceedings of The 2019 World Wide Web Conference, 450-458

\end{itemize}

% %----------------------------------------------------------------------------------------

% \vspace{0.2in} % Some whitespace between sections

% %----------------------------------------------------------------------------------------
% % MEMBERSHIPS SECTION
% %----------------------------------------------------------------------------------------

% \section{\centerline{MEMBERSHIPS}} \vspace{0.1in}

% \vspace{-5pt} % Reduce space between section title and contents

% \begin{center}
% American Psychological Association, Student Affiliate \\
% Vice President of Activities, RPI Weight-training Club \\
% Chairperson, Entertainment Committee, Utica College \\
% Latin-American Student Union, Utica College \\
% Member All-American Nautilus
% \end{center}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
% OPEN SOURCE
%----------------------------------------------------------------------------------------

\section{\centerline{OPEN SOURCE}} \vspace{0.1in}

See https://github.com/rijn for all the projects I contributed to.

{\sl iView} \hfill https://github.com/iview/iview\\
A UI components library for Vue.js.
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Wrote some components for it.
\item Bug fixes.
\end{itemize}

{\sl PHP-Verify-Code-Identification-Class} \hfill https://github.com/rijn/PHP-Verify-Code-Identification-Class\\
A native PHP class implementing some simple computer vision algorithms for character recognition.

{\sl Alipay Python SDK} \hfill https://github.com/lxneng/alipay\\
An Alipay API SDK for Python.

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
% HONORS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{HONORS \& AWARDS}} \vspace{0.1in}

{\sl Bronze Tablet 2018} \hfill Dec 2018 \\
University of Illinois at Urbana - Champaign, Champaign, IL, USA

{\sl LAS Fall 2017 Dean's List} \hfill Jan 2018 \\
University of Illinois at Urbana - Champaign, Champaign, IL, USA

{\sl LAS Spring 2017 Dean's List} \hfill Jun 2017 \\
University of Illinois at Urbana - Champaign, Champaign, IL, USA

{\sl LAS Fall 2016 Dean's List} \hfill Jan 2016 \\
University of Illinois at Urbana - Champaign, Champaign, IL, USA

{\sl First Prize in Collegiate Electronic Design Contest} \hfill Dec 2015 \\
Nanjing University of Posts and Telecommunications, Nanjing, Jiangsu, China

{\sl First Prize in Collegiate Electronic Design Contest} \hfill Dec 2014 \\
Nanjing University of Posts and Telecommunications, Nanjing, Jiangsu, China

{\sl First Prize in China Adolescents Science and Technology Innovation Contest} \hfill Jul 2014 \\
Ministry of Education of the People's Republic of China\\
China Association for Science and Techinology

{\sl Adolescents Technological Innovation Award in Province} \hfill Jul 2014 \\
People's Government of Jiangsu Province

Mao Yisheng Prize for Science and Technology

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
% INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{INTERESTS}} \vspace{0.1in}

\begin{center}
Algorithms, Software Engineering, Computer Vision, Artificial Intelligence, Machine Learning \\
Cooking, Photography, Lego
\end{center}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
% CITIZENSHIP
%----------------------------------------------------------------------------------------

\section{\centerline{CITIZENSHIP}} \vspace{0.1in}

\begin{center}
P.R.China
\end{center}

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}
