%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

% Setup the language.
% \usepackage[english]{babel}
% \hyphenation{Some-long-word}

\usepackage[margin=0.5in]{geometry} % Document margins
\usepackage{tabu}
\usepackage{booktabs}

\name{Yuanzhe Rijn(Ryan) Bian} % Your name
% \address{} % Your addess (optional)
\address{311 E White St Apt 30, Champaign, IL 61820 \\ (217)~$\cdot$~979~$\cdot$~1882 \\ bxbian951122@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Illinois at Urbana-Champaign} \hfill {August 2016 -- December 2018} \\
Bachelor of Engineering, Computer Science \hfill GPA: 3.98 \\
Dual Degree: Bachelor of Science, Mathematics

{\bf Nanjing University of Posts and Telecommunications(NUPT)} \hfill {September 2014 -- July 2016} \\
Bachelor of Science, Telecommunication Engineering (EE) \hfill GPA: 3.7

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{University of Illinois Research Park, EnterpriseWorks}{Jan 2018 - May 2018, Sep 2018 -- Dec 2018}{Software Engineer Internship}{Champaign, IL}
\item Designed manager system and SPA framework on Salesforce.
\end{rSubsection}

\begin{rSubsection}{Facebook}{May 2018 -- August 2018}{Software Engineer Internship}{Menlo Park, CA}
\item Worked on Spatial Computing Team. Helped to improve the geolocation data visualization tool.
\item Designed and implemented an augmented reality navigation x-plat App. Worked with indoor localization group and map generation group. Fulfilled the group plan two months ahead of schedule.
\end{rSubsection}

\begin{rSubsection}{NextCapital Group}{June 2017 -- December 2017}{Software Engineer Internship \& Remote Software Engineer Internship}{Chicago, IL}

\item Front-end group. Maintained NextCapital's front-end software which is written in Angular and React.
\item Upgraded the unit test framework. Result in $>50\%$ time saving on the CI by applying the new environment.
\item Developed an intelligent report generator which can help the manager generating weekly target completion report by analyzing data from the time tracker automatically.

\end{rSubsection}

\begin{rSubsection}{UmiUni}{February 2017 -- Present}{Co-founder \& CTO}{Champaign, IL}

\item Designed whole software architect. Participated and contributed to all projects, including design, programming, unit testing, code review and deployment planning. Developed back-end server powered by Node.js. Also developed front-end app by Vue.js, and contributed to the iOS App by RN.

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Dexta Robotics}{March 2014 -- August 2016}{Co-founder \& Electrical Engineer}{Nanjing, China}

\item Developed an embedded system for Dexmo. Built the website.
% \item Designed some steering motor circuit.

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Nanjing University of Posts and Telecommunications, Department of Publicity}{Apr 15 -- Jun 16}{Technical Adviser \& Develop Lead}{Nanjing, China}
\item Wrote a class that using computer vision and machine learning techniques to identify verification code.
\item Led a group to develop a load-balancing RESTFul API service and a web-app that has millions of PV/yr.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	Open Source Project
%----------------------------------------------------------------------------------------

\begin{rSection}{Open Source Project \& Research}{https://github.com/rijn}

\begin{tabu} to \textwidth {X X @{\hspace{1.5em}}}
{\bf iview/iview} & {\bf rijn/nodecho}\\
\begin{tabu}{@{}l@{}}
	UI components library with Vue.js. Main contributor. \\
	Over 15k people star or fork the repository.
\end{tabu}
&
\begin{tabu}{@{}l@{}}
	A single user blog system powered by Node.js.\\
	RESTFul API, Authorization, Markdown syntax.\\
\end{tabu}\\
\end{tabu}

\end{rSection}

%----------------------------------------------------------------------------------------
%	AWARD
%----------------------------------------------------------------------------------------

% \begin{rSection}{Honors and Awards}

% \begin{tabu} to \textwidth {@{} >{\bfseries}X l r @{\hspace{1.5em}}}
% First Prize in Collegiate Electronic Design Contest & NUPT & December 2014, 2015\\
% First Prize in China Adolescents Sci \& Tech Innovation Contest & CAST & July 2014
% \end{tabu}

% \end{rSection}

%----------------------------------------------------------------------------------------
%	Extracurricular Activities
%----------------------------------------------------------------------------------------

%\begin{rSection}{Extracurricular Activities}
%
%\begin{tabu} to \textwidth {@{} >{\bfseries}X X r @{\hspace{1.5em}}}
%Student Lecturer & NUPT & December 2014\\
%Design Lead & TEDx Event TEDxJinlingHighSchool & June 2012
%\end{tabu}
%
%\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Language and Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & C, C++, JavaScript, Node.js, Vue, React, React Native, Python, PHP, Verilog, \\
& Haskell, C\#, CoffeeScript\\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
